DATA 621 - Business Analytics and Data Mining

### 2020-11-21 Final_project/Draft_EDA_start.Rmd
Further updates to EDA

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE, warning=FALSE, message=FALSE)
```

@@

```{r load_data}
CA_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/CAvideos.csv"
CA_set <- read_csv(file = CA_path)
US_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/USvideos.csv"
US_set <- read_csv(file = US_path)
GB_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/GBvideos.csv"
GB_set <- read_csv(file = GB_path)
FR_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/FRvideos.csv"
FR_set <- read_csv(file = FR_path)
DE_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/DEvideos.csv"
DE_set <- read_csv(file = DE_path)
```

@@

The data contains the daily trending videos from 2017 with up to 200 listed 
trending videos per day.  We will be utilizing, at minimum, the json’s and 
CSV’s for Canada, United States, Great Britain, Germany and France, totaling 
30581 unique values.  The site has data for Japan, Mexico, Korea, India, and 
Russia; we will attempt to pull them in, if required, for a larger picture.  
However, the five already chosen datasets should be sufficient to cover the 
project statement.

@@

@@

```{r}
# Add Country Code to each set
# throw out incomplete cases
# Join all datasets into one large set - may use it may not
```

@@

```{r summary_ca}
summaryca <- CA_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summaryca)

@@

```{r summary_us}
summaryus <- US_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summaryus)

@@

```{r summary_us}
summarygb <- GB_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summarygb)

@@

```{r summary_fr}
summaryfr <- FR_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summaryfr)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE, warning=FALSE, message=FALSE)

#header-includes:
#    - \usepackage{setspace}
#    - \doublespacing
```

@@

```{r load_data}
ca_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/CAvideos.csv"
ca_set <- read_csv(file = ca_path)
us_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/USvideos.csv"
us_set <- read_csv(file = us_path)
gb_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/GBvideos.csv"
gb_set <- read_csv(file = gb_path)
fr_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/FRvideos.csv"
fr_set <- read_csv(file = fr_path)
de_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/DEvideos.csv"
de_set <- read_csv(file = de_path)
```

@@

We will be utilizing, at minimum, the json’s and CSV’s for Canada, 
United States, Great Britain, Germany and France, totaling 
30581 unique values.  The site has data for Japan, Mexico, Korea, India, and 
Russia; we will attempt to pull them in, if required, for a larger picture.  
However, the five already chosen datasets should be sufficient to cover the 
project statement.

@@

The datasets in total have 186,922 unique values across the 5 countries used. They 
contain the daily trending videos from 2017 with up to 200 listed trending videos 
per day.  The first response variable is coded as a 1 when a video's views are above 
the mean of views in their respective country and a 0 if they are below. The second 
response varible XXX is coded as a 1 for above the mean of the global population and 
0 if below.

In all, there are 8 predictors, which include:

Variables|Description   
-|----
views | The number of times a video was watched
category | the type of video, such as "Film & Animation", "Sports", "Music", etc... 
likes | the number of times a user clicked "like"
dislikes | the number of times a user clicked "dislike"
comment_count | the number of comments on an individual video   
comments_disabled | boolian value if the owner of the video disabled users from commenting   
ratings_disabled | boolian value if the owner of the video disabled ratings
country_code | code created to identify country of origin
view_target | Above (1) or below  (0) the mean views from country of origin
view_global_target | Above (1) or below  (0) the mean views globally

@@

```{r ca_data_prep}
ca_set <- ca_set %>% filter(complete.cases(ca_set))

ca_mean <- mean(ca_set$views)

ca_set <- ca_set%>%
  mutate(country = 'CA')%>%
  mutate(country_code = 1)%>%
  mutate(view_target = ifelse(views > ca_mean,1,0))
```

```{r de_data_prep}
de_set <- de_set %>% filter(complete.cases(de_set))

de_mean <- mean(de_set$views)

de_set <- de_set%>%
  mutate(country = 'DE')%>%
  mutate(country_code = 2)%>%
  filter(complete.cases(de_set))%>%
  mutate(view_target = ifelse(views > de_mean,1,0))
```

```{r fr_data_prep}
fr_set <- fr_set %>% filter(complete.cases(fr_set))

fr_mean <- mean(fr_set$views)

fr_set <- fr_set%>%
  mutate(country = 'FR')%>%
  mutate(country_code = 3)%>%
  filter(complete.cases(fr_set))%>%
  mutate(view_target = ifelse(views > fr_mean,1,0))
```

```{r gb_data_prep}
gb_set <- gb_set %>% filter(complete.cases(gb_set))

gb_mean <- mean(gb_set$views)

gb_set <- gb_set%>%
  mutate(country = 'GB')%>%
  mutate(country_code = 4)%>%
  filter(complete.cases(gb_set))%>%
  mutate(view_target = ifelse(views > gb_mean,1,0))
```

```{r us_data_prep}
us_set <- us_set %>% filter(complete.cases(us_set))

us_mean <- mean(us_set$views)

us_set <- us_set%>%
  mutate(country = 'US')%>%
  mutate(country_code = 5)%>%
  filter(complete.cases(us_set))%>%
  mutate(view_target = ifelse(views > us_mean,1,0))
```

```{r merge_datasets}
mergeCols = c('video_id','trending_date','title','channel_title','category_id','publish_time','tags','views','likes','dislikes','comment_count','thumbnail_link','comments_disabled','ratings_disabled','video_error_or_removed','description','country','country_code', 'view_target')

full_set <- ca_set %>% full_join(de_set, by=mergeCols)
full_set <- full_set %>% 
  full_join(fr_set, by=mergeCols)%>%
  full_join(gb_set, by=mergeCols)%>%
  full_join(us_set, by=mergeCols)

full_mean <- mean(full_set$views)

full_set <- full_set %>%
  mutate(view_global_target = ifelse(views > full_mean,1,0))
```

```{r global_target}
ca_set <- ca_set %>%
  mutate(view_global_target = ifelse(views > full_mean,1,0))

de_set <- de_set %>%
  mutate(view_global_target = ifelse(views > full_mean,1,0))

fr_set <- fr_set %>%
  mutate(view_global_target = ifelse(views > full_mean,1,0))

gb_set <- gb_set %>%
  mutate(view_global_target = ifelse(views > full_mean,1,0))

us_set <- us_set %>%
  mutate(view_global_target = ifelse(views > full_mean,1,0))
```

@@

```{r summary_ca}
summaryca <- ca_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summaryca)

@@

```{r summary_de}
summaryde <- de_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summaryus)

ggpairs(
  summaryde,
  lower = list(continuous = ggally_points, combo = ggally_dot_no_facet)
  )
us_corr <- cor(summaryde)
corrplot(us_corr, order = "hclust", tl.col = "black", tl.srt = 45, method = "ellipse", bg="black")

```{r summary_us}
summaryus <- us_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summaryus)

@@

```{r summary_us}
summarygb <- gb_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summarygb)

@@

```{r summary_fr}
summaryfr <- fr_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summaryfr)

@@

```{r summary_global}
summarygl <- full_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled)
describe(summarygl)

ggpairs(
  summarygl,
  lower = list(continuous = ggally_points, combo = ggally_dot_no_facet)
  )

fr_corr <- cor(summarygl)
corrplot(fr_corr, order = "hclust", tl.col = "black", tl.srt = 45, method = "ellipse", bg="black")
```

```{r}
